---
title: "Other countries"
author: "Cornelius Erfort"
date: "18 Aug 2021"
output: 
  pdf_document:
    dev: cairo_pdf
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, tidy.opts=list(width.cutoff = 80), tidy = T, python.reticulate = F)
knitr::opts_knit$set(root.dir = dirname(getwd()))

```

# Setting up

This script requires the files which are not included on GitHub.

## Loading packages

This script is based mainly on the functions of the quanteda package. For the cross-validation of the textmodels, quanteda.classifiers has to be loaded from GitHub.

```{r packages, message=FALSE, warning=FALSE, results='hide'}
start_time <- Sys.time()

packages <- c(
  "quanteda", "quanteda.textplots", "quanteda.textmodels", "quanteda.textstats", "quanteda.classifiers", "dplyr", "tm", "rmarkdown", "plyr", "readr", "ggplot2", "stringr", "formatR", "readstata13", "lubridate", "glmnet", "kableExtra", "stargazer", "tidyr", "extrafont", "openxlsx", "tools")

lapply(packages[!(packages %in% rownames(installed.packages()))], install.packages)

invisible(lapply(packages, require, character.only = T))

theme_update(text = element_text(family = "LM Roman 10")) # Set font family for ggplot

loadfonts()
loadfonts(device = "pdf")
source("scripts/functions.R")

seed <- 1621447882
set.seed(seed)

if(!dir.exists("other-countries")) dir.create("other-countries")

```

## Load the unlabeled data

```{r unlabeled, out.width = "80%"}
list.files("data/all")

unlabeled <- data.frame()

# if(file.exists("other-countries/unlabeled.RData")) load("other-countries/unlabeled.RData") else {
  for (country in list.files("data/all", full.names = T)) {
    print(country)
    load(country)
    unlabeled <- get(basename(country) %>% str_remove("\\.[:alpha:]*")) %>% 
      filter(!is.na(date)) %>% mutate(date = str_replace_all(date, "_", "-"),
                                      htext = str_c(header, " ", text)) %>%
      select(c(country, id, party, year, date, filepath, htext)) %>%
      rbind.fill(unlabeled)
  }
  
  table(unlabeled$country, useNA = "always")
  nrow(unlabeled)
  names(unlabeled)
  
  # Remove press releases without date
  unlabeled$date %>% ymd() %>% is.na() %>% table
  unlabeled$date <- ymd(unlabeled$date)
  unlabeled <- filter(unlabeled, !is.na(date))
  nrow(unlabeled)

  save(unlabeled, file = "other-countries/unlabeled.RData")
# }


table(unlabeled$country)

```


## Load the labeled data

```{r data, out.width = "80%"}
# Read the labeled data into one dataframe
labeled <- data.frame()

# if(file.exists("other-countries/labeled.RData")) load("other-countries/labeled.RData") else {
  for (country in list.files("data/labeled", full.names = T) %>% str_subset("(xlsx)|(csv)")) {
    
    if(file_ext(country) == "xlsx") {
      print("xlsx")
      print(country)
      labeled_c <- read.xlsx(country) 
      if(names(labeled_c) %>% str_detect("Spalte") %>% any()) labeled_c <- select(labeled_c, -c(starts_with("Spalte"))) 
      labeled <- labeled_c %>% 
        mutate(country = basename(country) %>% str_remove("-.*")) %>% 
        rbind.fill(labeled)
      print(nrow(labeled))
    } else {
      print("csv")
      print(country)
      labeled_c <- read.csv(country,
                          encoding = ifelse(str_detect(country, "spain"), "latin1", "unknown"),
                          sep = ",")
      if(names(labeled_c) %>% str_detect("Spalte") %>% any()) labeled_c <- labeled_c %>% select(-c(starts_with("Spalte")))
      labeled <- labeled_c  %>% 
        mutate(country = basename(country) %>% str_remove("-.*")) %>% 
        rbind.fill(labeled)
      print(nrow(labeled))
    } 
  }
  
  table(labeled$country, useNA = "always")
  nrow(labeled)
  
  names(labeled)
  
  labeled <- filter(labeled, !is.na(date))

  
  # Tidy date
  labeled$date[substr(labeled$date, 5, 5) == "-"] <- labeled$date[substr(labeled$date,   5, 5) == "-"] %>% ymd()
  labeled$date[substr(labeled$date, 3, 3) %in% c("-", "/")] <-   labeled$date[substr(labeled$date, 3, 3) %in% c("-", "/")] %>% dmy()
  labeled$date <- labeled$date %>% as.numeric() %>% as.Date(origin = "1970-01-01")
  nrow(labeled)
  
  labeled <- filter(labeled, !is.na(date))

  
  # Tidy issue
  # labeled$issue[is.na(labeled$issue)] <- labeled$Issue[is.na(labeled$issue)]
  # labeled$issue[is.na(labeled$issue)] <-   labeled$X1st.coding..issue[is.na(labeled$issue)]
  labeled$issue <- str_replace_all(labeled$issue, c("19a" = "191", "19b" =  "192", "2 or 192" = "2", "98 or 191" = "98", "201" = "20", "145" = "14", "19$" = "191"))
  labeled$issue <- ifelse(labeled$issue %in% c("0", "."), NA, labeled$issue)

  labeled$issue %>% unique %>% sort
  labeled$issue %>% unique %>% sort %>% length
  filter(labeled, country == "germany")$issue %>% unique %>% sort %>% length

  table(labeled$issue, useNA = "always")
  labeled <- filter(labeled, !is.na(issue) & issue != ".")
  
  save(labeled, file = "other-countries/labeled.RData")
# }


table(labeled$country, useNA = "always")

# Subset to relevant vars
textpress <- labeled %>% select("country", "header", "text", "issue", "party", "date", "id")
# rm(labeled)

# Remove non-thematic press releases
# textpress <- textpress %>% filter(issue != 98)
nrow(textpress)

```

## Prepare data


```{r categories}
textpress$issue <- as.numeric(textpress$issue)
textpress$htext <- str_c(textpress$header, " ", textpress$text)

# Make order of documents random
textpress <- textpress[sample(1:nrow(textpress), nrow(textpress)), ]

# Add folds variable for cross-validation (stratified by country)
textpress_old <- textpress
textpress <- data.frame()

for (country in unique(textpress_old$country)) {
  
  text_country <- textpress_old[textpress_old$country == country, ]
  
  ind = sample(rep(1:5,each = nrow(text_country)/5))
  ind <- c(ind, rep(NA, nrow(text_country)-length(ind)))
  text_country$cv_sample <- ind
  textpress <- rbind.fill(textpress, text_country)

  }

table(textpress$country, textpress$cv_sample)
if(!file.exists("other-countries/textpress.RData")) save(textpress, file = "other-countries/textpress.RData")

str_c(labeled$country, labeled$id) %in% str_c(unlabeled$country, unlabeled$id) %>% table # All IDs from the labeled data are also in the unlabeled!

# labeled[!(str_c(labeled$country, labeled$id) %in% str_c(unlabeled$country, unlabeled$id)), ] %>% View
# labeled[!(str_c(labeled$country, labeled$id) %in% str_c(unlabeled$country, unlabeled$id)), ]$country %>% table

# str_c(labeled$country, labeled$id) %in% str_c(unlabeled$country, unlabeled$id) %>% table

alldocs <- merge(unlabeled, select(textpress, c(country, id, issue, cv_sample)), by = c("country", "id"), all.x = T)

# Export list of parties


parties_coding <- unique(select(alldocs, c(country, party)))
parties_coding <- parties_coding[order(parties_coding$country, parties_coding$party), ]
write.xlsx(parties_coding, "other-countries/parties-export.xlsx")

```


# Ridge (L2)

```{r tm-ridge}

corp_press <- corpus(textpress$htext,
                       docvars = select(textpress, c(country, issue, party, cv_sample)))

ridge_eval <- data.frame()

for (country in unique(corp_press$country)[4:8]) {
  print(country)
  
  corp_country <- corp_press[corp_press$country == country, ]

  # Create alternative dfm (bigrams and tfidf)
  dfmat_alt <- corpus_subset(corp_country) %>%
    tokens() %>% tokens_ngrams(n = 1:2) %>%
    dfm(remove = ifelse(country == "poland", stopwords::stopwords("pl", source = "stopwords-iso"), stopwords(str_replace_all(country, c("germany" = "de", "austria" = "de", "spain" = "es", "netherlands" = "nl", "ireland" = "en", "sweden" = "sw", "denmark" = "da")))), # Stem and remove stopwords, punctuation etc.
        remove_punct = T, remove_number = T, remove_symbols = T, remove_url =   T) %>% dfm_wordstem(language = str_replace_all(country, c("germany" = "de", "austria" = "de", "spain" = "es", "netherlands" = "nl", "ireland" = "en", "sweden" = "sw", "denmark" = "da", "poland" = "pl"))) %>%
    dfm_trim(max_docfreq = .06, # Remove words occurring >6% of docs
             docfreq_ = "prop") %>%
     dfm_trim(min_docfreq = 5, # Remove words occurring in <5 docs
             docfreq_ = "count") %>%
    suppressWarnings()
  
  ridge_eval <- textmodel_evaluate(dfmat_alt, dfmat_alt$issue, k = 5, model = "textmodel_svm", fun = "accuracy", seed = seed, parameters = list(type = 7)) %>% dplyr::mutate(country = country) %>% rbind.fill(ridge_eval)
  print(ridge_eval$accuracy[ridge_eval$country == country] %>% max)
}

aggregate(cbind(time, accuracy) ~ country + seed, ridge_eval, mean) %>% View



```

# Transformers

BETO, Multi-lingual.

```{r transfer}
names(textpress)

# Show distribution of text length
sapply(textpress$htext, str_length) %>% density(na.rm = T) %>% plot

# Count words/tokens
sapply(textpress$htext, function(x) lengths(gregexpr("\\W+", x)) + 1) %>% max # max_seq_length = 512

# Add labels 0-22 (instead of CAP labels)
labels <- data.frame(issue = unique(alldocs$issue) %>% sort, label = c(0:22))
alldocs <- merge(alldocs, labels, by = "issue", all.x = T)

nrow(alldocs)

# Write to csv
select(alldocs, c(htext, label, cv_sample, country, id)) %>% write.csv("other-countries/alldocs.csv", row.names = F)

```

# Add labels from Transformers model
# And Parlgov IDs
# And hand-coded labels

We run a multilingual model in Python and add the predicted labels to our dataframe here.

```{r add-labels}
load("other-countries/unlabeled.RData")
alldocs_pred <- read_csv("other-countries/alldocs-pred.csv", 
    col_names = FALSE, col_types = cols(X1 = col_integer(), 
        X3 = col_integer())) %>%
  dplyr::rename(label = X1, country = X2, id = X3, issue_pred_name = X4, issue_pred = X5)


unlabeled$id <- as.numeric(unlabeled$id)

alldocs_lab <- merge(unlabeled, alldocs_pred, by = c("country", "id"))

parties <- read.xlsx("other-countries/parties-import.xlsx") %>% select(-c(country)) %>% dplyr::rename(country = country_name, party_abbr = party, party = X6) %>% unique
parties <- parties[!duplicated(select(parties, c(country, party))), ]

alldocs_lab <- merge(alldocs_lab, parties, all.x = T, by = c("country", "party"))

alldocs_lab$parlgov_id %>% table(useNA = "always")

(alldocs_lab %>% filter(is.na(parlgov_id))) %>% select(country, party) %>% unique # poland - wis does not have a parlgov_id (is also not in the polls data)

load("other-countries/labeled.RData")
labeled <- select(labeled, c(country, id, issue, position))
alldocs_lab <- merge(alldocs_lab, labeled, all.x = T, by = c("country", "id"))

save(alldocs_lab, file = "other-countries/alldocs_lab.RData")
alldocs_lab_notxt <- select(alldocs_lab, -c(htext))
save(alldocs_lab_notxt, file = "other-countries/alldocs_lab_notxt.RData")

```

# Identifiers
country         - Country
party           - Party name used in our data management (e.g. afd_fraktion/afd_bundesverband, fdp_fraktion/fdp_bundesverband are separate here but not in the vars below)
parlgov_id
party_abbr      - Party abbreviation from Parlgov
party_name      - Party name from Parlgov
year            - Year of publication of press release
date            - Date of publication of press release
filepath        - Local file path where the file is stored

# Content
htext           - Header and text of press release

# Issue
issue           - Hand coded issue (1, 2,...,19.1, 19.2, 98, 99) (not available for all obs)
issue_pred      - Issue predicted by the multilingual Transformer model
issue_pred_name - Name of predicted issue category (e.g. "Macroeconomics")
label           - Issue codes/labels used in Transformer model (0-23)
position        - Hand coded position (not available for all obs)

```{r evaluate-multilingual}

bert_pred <- read_csv("other-countries/bert-pred.csv", col_names = F)
names(bert_pred) <- c("prediction", "label", "cv_sample", "id", "country")

table(bert_pred$prediction == bert_pred$label)/nrow(bert_pred)



table(bert_pred$prediction == bert_pred$label, bert_pred$country)  %>% t %>% data.frame() %>% pivot_wider(names_from = "Var2", values_from = "Freq") %>% mutate(sum = `FALSE` + `TRUE`, `FALSE` = `FALSE`/sum, `TRUE` = round(`TRUE`/sum, 3)) %>% dplyr::rename(Accuracy = `TRUE`, Country = Var1) %>% select(c(Country, Accuracy)) %>% mutate(Country = str_to_title(Country)) %>% stargazer(summary = F, rownames = F)
```

