---
title: "Application to unlabeled data"
author: "Cornelius Erfort"
date: "8/5/2021"
output: 
  pdf_document:
    dev: cairo_pdf
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, tidy.opts=list(width.cutoff = 80), tidy = T, python.reticulate = F)
knitr::opts_knit$set(root.dir = dirname(getwd()))
```

# Summary

We predict issue labels for all unlabeled German press releases and calculate the share of press releases dedicated to each issue area for each quarter.

# Setting up

This script requires the files which are not included on GitHub.

At the end of this script, the file "issue_agendas.RData" is saved. It contains quarterly estimates for the share of press releases for each issue and party.

## Loading packages

```{r packages, message=FALSE, warning=FALSE, results='hide'}
start_time <- Sys.time()

packages <- c(
  "quanteda", "quanteda.textmodels", "dplyr", "caret", "randomForest", "tm", "rmarkdown", "plyr", "readr", "ggplot2", "stringr", "formatR", "readstata13", "lubridate", "reticulate", "doMC", "glmnet", "kableExtra", "stargazer", "extrafont", "ggrepel")

lapply(packages[!(packages %in% rownames(installed.packages()))], install.packages)

if(!("quanteda.classifiers" %in% rownames(installed.packages()))) {
  remotes::install_github("quanteda/quanteda.classifiers")
} 

invisible(lapply(c(packages, "quanteda.classifiers"), require, character.only = T))

loadfonts()
loadfonts(device = "pdf")
theme_update(text = element_text(family = "LM Roman 10")) # Set font family for ggplot

source("scripts/functions.R")

load("files/press.RData")

```

# Load the database

# Visualize issue agendas

```{r}

# Imm
for (this_country in unique(issue_agendas$country) %>% sort) {

  plot_data <- filter(issue_agendas, country == this_country & issue == 9)
  
  plot_data <- filter(plot_data, party_sum > 5)
  
  thisplot <- ggplot(plot_data, aes(x = date, y = attention)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
          axis.text.y = element_text(size = 14),
          axis.title = element_text(size = 14),
          text = element_text(size = 14)) +
    scale_x_date(date_breaks = "2 years", date_labels = "%Y", limits = c(plot_data$date %>% min, plot_data$date %>% max)
) +
    ylab("Share of press releases per quarter") +
    xlab("")
  
  thisplot <- thisplot +
        geom_step(color = "dark grey", alpha = .8) +
        #geom_smooth(method = "loess", formula = "y ~ x", color = "dark grey", lty = 2, se = F, alpha = .3)
        geom_line(stat="smooth", method = "loess", formula = "y ~ x",
                size = .7,
                linetype ="dashed",
                alpha = 0.8, color = "black",
                se = F)
  
  if(min(plot_data$attention) >= 0) thisplot <- thisplot + ylim(c(0, NA))
  

    thisplot <- thisplot +
      geom_vline(xintercept = ymd("2015-08-31"), color = "dark grey", lty = 2)
  
  thisplot <- thisplot + facet_wrap(~ party) + theme(strip.text.x = element_text(size = 15))
  
  thisplot
  
    ggsave(str_c("plots/immigration-agenda-", this_country,".pdf"), device = cairo_pdf, width = 5*2^.5, height = 5)

}

# Housing
for (this_country in "germany" %>% sort) {

  plot_data <- filter(issue_agendas, country == this_country & issue == 14)
  
  plot_data <- filter(plot_data, party_sum > 5)
  
  thisplot <- ggplot(plot_data, aes(x = date, y = attention)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
          axis.text.y = element_text(size = 14),
          axis.title = element_text(size = 14),
          text = element_text(size = 14)) +
    scale_x_date(date_breaks = "2 years", date_labels = "%Y", limits = c(plot_data$date %>% min, plot_data$date %>% max)
) +
    ylab("Share of press releases per quarter") +
    xlab("")
  
  thisplot <- thisplot +
        geom_step(color = "dark grey", alpha = .8) +
        #geom_smooth(method = "loess", formula = "y ~ x", color = "dark grey", lty = 2, se = F, alpha = .3)
        geom_line(stat="smooth", method = "loess", formula = "y ~ x",
                size = .7,
                linetype ="dashed",
                alpha = 0.8, color = "black",
                se = F)
  
  if(min(plot_data$attention) >= 0) thisplot <- thisplot + ylim(c(0, NA))
  

    thisplot <- thisplot +
      geom_vline(xintercept = ymd("2013-09-22"), color = "dark grey", lty = 2) +
            geom_vline(xintercept = ymd("2017-09-24"), color = "dark grey", lty = 2) +
      ylim(c(0,0.075))

  
  thisplot <- thisplot + facet_wrap(~ party) + theme(strip.text.x = element_text(size = 15))
  
  thisplot
  
    ggsave(str_c("plots/housing-agenda-", this_country,".pdf"), device = cairo_pdf, width = 5*2^.5, height = 5)

}

```





```{r script_eval}
# Time needed to run script
print(Sys.time() - start_time) 

