---
title: "PARTYPRESS datasets and variables"
# author: "Cornelius Erfort, Lukas F. Stoetzer, Heike Klüver"
# thanks: 'Research for this contribution is part of the Cluster of Excellence "Contestations of the Liberal Script" (EXC 2055, Project-ID: 390715649), funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany\textquotesingle s Excellence Strategy. We thank Leonie Fuchs, Paul Bochtler, Daniel Cruz, Johannes Lattmann, Felix Heimburger,  Violeta Haas and Tim Wappenhans for valuable research assistance. Replication material can be found on \texttt{\href{https://github.com/cornelius-erfort/scripts-issue-agendas}{https://github.com/cornelius-erfort/scripts-issue-agendas}.}\vspace{5mm}'
date: "2022-11-18"
output: 
  pdf_document:
    # extra_dependencies: ["tabularx", "textcomp", "tikz", "pgf"]
    toc: true
    toc_depth: 1
    includes:
            in_header: inheader.sty
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_knit$set(root.dir = "publication/rds")
library(stargazer)
library(dplyr)
library(stringr)

```



\newpage
# Main dataset PARTYPRESS

Load files \path{partypress.csv} (67MB) or \path{partypress.RDS} (9MB) or \path{partypress.dta} (600MB).

### Variables
\renewcommand{\arraystretch}{1}
\begin{tabularx}{\textwidth}{llX}

\textbf{Variable name} & \textbf{Format} & \textbf{Description} \\

\hline

\path{country_name}          &   [string]         &   Name of the country in small caps  \\
\path{id}                    &   [integer]        &   Press release identifier, unique within \path{country_name}  \\
\path{parlgov_id}            &   [integer]        &   Party ID (merge with \path{party_id} in ParlGov) \\
\path{party}                 &   [string]         &   Abbreviation of the party name (ParlGov) \\
\path{party_name}            &   [string]         &   Party name (ParlGov) \\
\path{party_name_english}    &   [string]         &   Party name in English (ParlGov) \\
\path{family_name}           &   [string]         &   Party family name (ParlGov) \\

\hline

\path{header}                &   [string]         &   Header of the press release in original language   \\
\path{date}                  &   [date]         &   Issue date of the press release  \\
\path{month}                 &   [yyyymm]      &   Issue month of the press release  \\
\path{month_start}           &   [date]            &   Date of the first day of the month  \\
\path{month_end}             &   [date]             &   Date of the last day of the month \\
\path{week_start}            &   [date]             &   Date of previous Monday  \\
\path{week_end}              &   [date]             &   Date of following Sunday \\
\path{calendar_week}         &   [integer, 1-53]  &   Calendar week  \\

\hline


\path{issue_multi}           &   [integer, 1-23]        &   Issue category predicted from Multilingual Transformer using all labeled docs from all countries  \\
\path{issue_mono}           &   [integer, 1-23]        &   Issue category predicted from Monolingual Transformer using only labeled docs from one countries  \\


\path{issue_ridge}           &   [integer, 1-23]        &   Issue category predicted from Ridge models, separate models by country \\
\path{issue_super}           &   [integer, 1-23]        &   Issue category predicted from SuperLearner models, separate models by country \\


\hline

\path{issue_coder}           &   [integer, 1-23]        &   Issue category hand coded by first or second country expert coder  \\
\path{issue_coder2}          &   [integer, 1-23]         &   Issue category hand coded by second country expert coder, only for texts coded by both coders  \\

\hline


\path{position_coder}        &   [integer, 1-2]        &   Position of press release, hand coded by one country expert coder, 1 pro, 2 anti \\
\path{position_coder2}       &   [integer, 1-2]        &   Position of press release, hand coded by 2nd country expert coder, only for texts coded by both coders, 1 pro, 2 anti \\
\path{cv_sample}             &   [integer]         &   Folds used in cross validation, $k = 1,...,5$, not used: $-1$ \\


\end{tabularx}
\vfill
### Sample

```{r echo=TRUE}
partypress <- readRDS("rds/partypress.RDS")
partypress[sample(1:nrow(partypress), 5), ] %>% select(country_name, id, 
                                                       parlgov_id, party, 
                                                       date, issue_multi)
```

\vfill

\newpage
# Issue names dataset PARTYPRESS ISSUES
Load files \path{partypress_issues.csv} (1KB) or \path{partypress_issues.RDS} (1KB) or \path{partypress_issues.dta} (3KB).

This dataset provides the issue category names for merging. Merge via one of the \path{issue_*} variables.



### Variables
\begin{tabularx}{\textwidth}{llX}

\textbf{Variable name} & \textbf{Format} & \textbf{Description} \\

\hline

\path{issue}          &   [integer, 1-23]         &   Issue category code  \\
\path{issue_name}     &   [string]        &   Issue category description  \\


\end{tabularx}

\vfill
### Issue list
```{r echo=TRUE}
partypress_issues <- readRDS("rds/partypress_issues.RDS")
partypress_issues
```

\vfill
\newpage

# Raw texts dataset PARTYPRESS TEXTS
Load files \path{partypress_texts.csv} (561MB) or \path{partypress_texts.RDS} (193MB) (not available as \path{.dta}).

This dataset provides the raw texts of all press releases. The headers are contained in the main dataset.
We provide the texts separately because they use a lot of disk space but some users may not be interested in raw text. Merge via \path{country_name} + \path{id}.

### Variables
\begin{tabularx}{\textwidth}{llX}

\textbf{Variable name} & \textbf{Format} & \textbf{Description} \\

\hline

\path{country_name}          &   [string]         &   Name of the country in small caps  \\
\path{id}                    &   [integer]        &   Press release identifier, unique within \path{country_name}  \\
\path{text}                  &   [string]         &   Text of press releases in original language\\

\end{tabularx}

\vfill

### Sample

```{r}
partypress_texts <- readRDS("rds/partypress_texts.RDS")
partypress_texts[sample(1:nrow(partypress_texts), 10), ] %>% 
  mutate(text = substr(text, 1, 60) %>% str_c("(...)")) %>% 
  select(country_name, id, text)
```

\vfill

\newpage
# Aggregated datasets MONTHLY and WEEKLY AGENDAS
Load files \path{monthly_agendas.csv} (20MB)/\path{weekly_agendas.csv} (69MB) or \path{monthly_agendas.RDS} (1MB)/\path{weekly_agendas.RDS} (3MB)  or \path{monthly_agendas.dta} (31MB)/\path{weekly_agendas.dta} (117MB).

### Variables
\begin{tabularx}{\textwidth}{llX}

\textbf{Variable name} & \textbf{Format} & \textbf{Description} \\

\hline

\path{country_name}          &   [string]         &   Name of the country in small caps  \\
\path{parlgov_id}            &   [integer]        &   Party ID (merge with \path{party_id} in ParlGov) \\
\path{party}                 &   [string]         &   Abbreviation of the party name (ParlGov) \\
\path{party_name}            &   [string]         &   Party name (ParlGov) \\
\path{party_name_english}    &   [string]         &   Party name in English (ParlGov) \\
\path{family_name}           &   [string]         &   Party family name (ParlGov) \\
\hline


\multicolumn{3}{l}{only in \path{monthly_agendas}:} \\
\path{month}                 &   [yyyymm]      &   Month   \\
\path{month_start}           &   [date]            &   Date of the first day of the month  \\
\path{month_end}             &   [date]             &   Date of the last day of the month \\
\hline

\multicolumn{3}{l}{only in \path{weekly_agendas}:} \\
\path{calendar_week}         &   [integer, 1-53]  &   Calendar week  \\
\path{week_start}            &   [date]             &   Date of previous Monday  \\
\path{week_end}              &   [date]             &   Date of following Sunday \\

\hline

\path{issue}           &   [integer]        &   Issue category  \\

\path{issue_descr}           &   [string]        &    Issue category description \\

\hline


\path{share_multi}            &   [numeric]        &   Share of press releases of category \path{issue} of all \path{party_sum} predicted from Multilingual Transformer using all labeled docs from all countries \\
\path{share_mono}            &   [numeric]        &   Share of press releases of category \path{issue} of all \path{party_sum} predicted from Monolingual Transformer using all labeled docs from each country in separate models \\
\path{share_ridge}            &   [numeric]        &   Share of press releases of category \path{issue} of all \path{party_sum} predicted from Ridge using all labeled docs from each country in separate models \\
\path{share_super}            &   [numeric]        &   Share of press releases of category \path{issue} of all \path{party_sum} predicted from SuperLearner using all labeled docs from each country in separate models \\



\path{party_sum}            &   [integer]        &   Total number of press releases by this party in this month/week \\


\end{tabularx}

\newpage

### Samples

```{r echo=TRUE}
monthly_agendas <- readRDS("rds/monthly_agendas.RDS")
monthly_agendas[sample(1:nrow(monthly_agendas), 10), ] %>% 
  select(country_name, parlgov_id, party, month, issue, 
         share_multi)

```
\vfill

```{r echo=TRUE}
weekly_agendas <- readRDS("rds/weekly_agendas.RDS")
weekly_agendas[sample(1:nrow(weekly_agendas), 10), ] %>% 
  select(country_name, parlgov_id, party, week_start, 
         issue, share_multi)
```

\vfill