---
title: "PARTYPRESS datasets and variables"
author: "Cornelius Erfort, Lukas F. Stoetzer, Heike Klüver"
thanks: 'We are grateful for valuable comments and suggestions by Eri Bertsou and excellent research assistance by Paul Bochtler, Daniel Cruz, Leonie Fuchs, Violeta Haas, Felix Heimburger, Johannes Lattmann, and Tim Wappenhans. Research for this contribution is part of the Cluster of Excellence "Contestations of the Liberal Script" (EXC 2055, Project-ID: 390715649), funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany´s Excellence Strategy. Cornelius Erfort is moreover grateful for generous funding provided by the DFG through the Research Training Group DYNAMICS (GRK 2458/1).\vspace{5mm}'
date: "2023-02-06"
output: 
  pdf_document:
    # extra_dependencies: ["tabularx", "textcomp", "tikz", "pgf", "pgfplots"]
    toc: true
    toc_depth: 1
    includes:
            in_header: inheader.sty
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_knit$set(root.dir = "publication/rds")
library(stargazer)
library(dplyr)
library(stringr)

```

\newpage

# Overview

This document is designed to facilitate the use of the PARTYPRESS database. \autoref{fig:data-structure} visualizes how the different datasets are connected. For each dataset the following sections provide an overview of variables with a description.

There are five different datasets. First, the main dataset \textit{PARTYPRESS} that provides information about each individual press release in our database, e.g. issuing party or date. Second, \textit{PARTYPRESS ISSUES} provides all issues used for classification; it can be merged to the other datasets. Third, \textit{PARTYPRESS TEXTS} provides the full texts for each press release (the main dataset only contains the header); it can be merged to the main dataset. Fourth, \textit{MONTHLY AGENDAS} provides data from the main dataset aggregated to calendar months. Fifth, \textit{WEEKLY AGENDAS} provides data from the main dataset aggregated to calendar weeks.

\footnotetext[1]{\label{note1} The text and header of the press releases will be published after permission has been granted by the copyright holders.}

\begin{figure}[!ht]
\caption{Data structure}\label{fig:data-structure}
\begin{tikzpicture}[node distance=.5cm]
\tikzstyle{normal} = [rectangle, minimum width=2.5cm, minimum height=.5cm,text centered, draw=black]
\tikzstyle{title} = [minimum width=2.5cm, minimum height=.5cm,text centered]
\node (core-0) [title, xshift = -3.1cm, yshift = 2cm] {\textit{Main}};
\node (core-1) [normal, below of=core-0] {\path{country_name}};
\node (core-2) [normal, below of=core-1] {\path{id}};
\node (core-3) [normal, below of=core-2] {\path{parlgov_id}};
\node (core-4) [normal, below of=core-3] {\path{party_name}};
\node (core-5) [normal, below of=core-4] {\path{header}*};
\node (core-6) [normal, below of=core-5] {\path{date}};
\node (core-7) [normal, below of=core-6] {\path{month_start}};
\node (core-8) [normal, below of=core-7] {\path{week_start}};
\node (core-9) [normal, below of=core-8] {\path{issue_multi}};
\node (core-10) [normal, below of=core-9] {\path{issue_mono}};
\node (core-11) [normal, below of=core-10] {\path{issue_ridge}};
\node (core-12) [normal, below of=core-11] {\path{issue_super}};
\node (core-13) [normal, below of=core-12] {\path{issue}};
\node (core-14) [normal, below of=core-13] {\path{position}};
\node (core-15) [normal, below of=core-14] {\path{...}};
\node (text-0) [title, left of=core-0, xshift = -4cm] {\textit{Texts}};
\node (text-1) [normal, below of=text-0] {\path{country_name}};
\node (text-2) [normal, below of=text-1] {\path{id}};
\node (text-3) [normal, below of=text-2] {\path{text}*};
\node (issue-0) [title, below of=text-3, yshift=-8cm] {\textit{Issues}};
\node (issue-1) [normal, below of=issue-0] {\path{issue}};
\node (issue-2) [normal, below of=issue-1] {\path{issue_name}};
\draw[->, rounded corners=4mm] (core-1.west) -- (text-1.east);
\draw[->, rounded corners=4mm] (core-2.west) -- (text-2.east);
\draw [fill=white] (core-1.west) circle[radius= 0.2 em]; 
\draw [fill=white] (core-2.west) circle[radius= 0.2 em]; 
\draw[, rounded corners=4mm] (core-9.west) -| ++(-.5,-.8) ;
\draw[, rounded corners=4mm] (core-10.west) -| ++(-.5,-.8) ;
\draw[, rounded corners=4mm] (core-11.west) -| ++(-.5,-.8) ;
\draw[, rounded corners=4mm] (core-12.west) -| ++(-.5,-.8) ;
\draw[->, rounded corners=4mm] (core-13.west) -| ++(-.5,-1) |-  (issue-1.east);
\draw [fill=white] (core-9.west) circle[radius= 0.2 em]; 
\draw [fill=white] (core-10.west) circle[radius= 0.2 em]; 
\draw [fill=white] (core-11.west) circle[radius= 0.2 em]; 
\draw [fill=white] (core-12.west) circle[radius= 0.2 em]; 
\draw [fill=white] (core-13.west) circle[radius= 0.2 em]; 
\node (monthly-0) [title, right of=core-0, xshift = 6cm, yshift = 0cm] {\textit{Monthly}};
\node (monthly-1) [normal, below of=monthly-0] {\path{country_name}};
\node (monthly-2) [normal, below of=monthly-1] {\path{parlgov_id}};
\node (monthly-3) [normal, below of=monthly-2] {\path{party_name}};
\node (monthly-4) [normal, below of=monthly-3] {\path{month_start}};
\node (monthly-5) [normal, below of=monthly-4] {\path{issue}};
\node (monthly-6) [normal, below of=monthly-5] {\path{share_multi}};
\node (monthly-7) [normal, below of=monthly-6] {\path{share_mono}};
\node (monthly-8) [normal, below of=monthly-7] {\path{share_ridge}};
\node (monthly-9) [normal, below of=monthly-8] {\path{share_super}};
\node (monthly-10) [normal, below of=monthly-9] {\path{party_sum}};
\node (monthly-11) [normal, below of=monthly-10] {\path{...}};
\node (line) [title, left of=monthly-4, xshift = -2.5cm, yshift = .25cm] {aggregated};
\node (line) [title, left of=monthly-4, xshift = -2.5cm, yshift = -.25cm] {by month};
\node (weekly-0) [title, below of=monthly-9, xshift = 0cm, yshift = -1.5cm] {\textit{Weekly}};
\node (weekly-1) [normal, below of=weekly-0] {\path{country_name}};
\node (weekly-2) [normal, below of=weekly-1] {\path{parlgov_id}};
\node (weekly-3) [normal, below of=weekly-2] {\path{party_name}};
\node (weekly-4) [normal, below of=weekly-3] {\path{week_start}};
\node (weekly-5) [normal, below of=weekly-4] {\path{issue}};
\node (weekly-6) [normal, below of=weekly-5] {\path{share_multi}};
\node (weekly-7) [normal, below of=weekly-6] {\path{share_mono}};
\node (weekly-8) [normal, below of=weekly-7] {\path{share_ridge}};
\node (weekly-9) [normal, below of=weekly-8] {\path{share_super}};
\node (weekly-10) [normal, below of=weekly-9] {\path{party_sum}};
\node (weekly-11) [normal, below of=weekly-10] {\path{...}};
\node (line) [title, left of=weekly-4, xshift = -2.5cm, yshift = .25cm] {aggregated};
\node (line) [title, left of=weekly-4, xshift = -2.5cm, yshift = -.25cm] {by week};
\draw[->, rounded corners=4mm] (core-7.east) -| ++(.5,.75)  |- (monthly-4.west);
\draw[->, rounded corners=4mm] (core-8.east) -| ++(.5,-1)  |- (weekly-4.west);
\draw [fill=white] (core-7.east) circle[radius= 0.2 em]; 
\draw [fill=white] (core-8.east) circle[radius= 0.2 em]; 
\draw[->, rounded corners=4mm] (weekly-5.west)  -| ++(-.5,-.75)  |- (issue-1.east);
\draw[, rounded corners=4mm] (monthly-5.west) -| ++(-.5,-6.8) ;
\draw [fill=white] (weekly-5.west) circle[radius= 0.2 em]; 
\draw [fill=white] (monthly-5.west) circle[radius= 0.2 em]; 
\end{tikzpicture}
\end{figure}



\newpage
\footnotetext[1]{\label{note1} The text and header of the press releases will be published after permission has been granted by the copyright holders.}

# Main dataset PARTYPRESS

Load files \path{partypress.csv} (67MB) or \path{partypress.RDS} (9MB) or \path{partypress.dta} (600MB).


### Variables
\renewcommand{\arraystretch}{1}
\begin{tabularx}{\textwidth}{llX}

\textbf{Variable name} & \textbf{Format} & \textbf{Description} \\

\hline

\path{country_name}          &   [string]         &   Name of the country in small caps  \\
\path{id}                    &   [integer]        &   Press release identifier, unique within \path{country_name}  \\
\path{parlgov_id}            &   [integer]        &   Party ID (merge with \path{party_id} in ParlGov) \\
\path{party}                 &   [string]         &   Abbreviation of the party name (ParlGov) \\
\path{party_name}            &   [string]         &   Party name (ParlGov) \\
\path{party_name_english}    &   [string]         &   Party name in English (ParlGov) \\
\path{family_name}           &   [string]         &   Party family name (ParlGov) \\

\hline

\path{header}*                &   [string]         &   Header of the press release in original language \\
\path{date}                  &   [date]         &   Issue date of the press release  \\
\path{month}                 &   [yyyymm]      &   Issue month of the press release  \\
\path{month_start}           &   [date]            &   Date of the first day of the month  \\
\path{month_end}             &   [date]             &   Date of the last day of the month \\
\path{week_start}            &   [date]             &   Date of previous Monday  \\
\path{week_end}              &   [date]             &   Date of following Sunday \\
\path{calendar_week}         &   [integer, 1-53]  &   Calendar week  \\

\hline


\path{issue_multi}           &   [integer, 1-23]        &   Issue category predicted from Multilingual Transformer using all labeled docs from all countries  \\
\path{issue_mono}           &   [integer, 1-23]        &   Issue category predicted from Monolingual Transformer using only labeled docs from one countries  \\


\path{issue_ridge}           &   [integer, 1-23]        &   Issue category predicted from Ridge models, separate models by country \\
\path{issue_super}           &   [integer, 1-23]        &   Issue category predicted from SuperLearner models, separate models by country \\


\hline

\path{issue_coder}           &   [integer, 1-23]        &   Issue category hand coded by first or second country expert coder  \\
\path{issue_coder2}          &   [integer, 1-23]         &   Issue category hand coded by second country expert coder, only for texts coded by both coders  \\

\hline


\path{position_coder}        &   [integer, 1-2]        &   Position of press release, hand coded by one country expert coder, 1 pro, 2 anti \\
\path{position_coder2}       &   [integer, 1-2]        &   Position of press release, hand coded by 2nd country expert coder, only for texts coded by both coders, 1 pro, 2 anti \\
\path{cv_sample}             &   [integer]         &   Folds used in cross validation, $k = 1,...,5$, not used: $-1$ \\


\end{tabularx}
\vfill
### Sample

```{r echo=TRUE}
partypress <- readRDS("rds/partypress.RDS")
partypress[sample(1:nrow(partypress), 5), ] %>% select(country_name, id, 
                                                       parlgov_id, party, 
                                                       date, issue_multi)
```

\vfill

\newpage
# Issue names dataset PARTYPRESS ISSUES
Load files \path{partypress_issues.csv} (1KB) or \path{partypress_issues.RDS} (1KB) or \path{partypress_issues.dta} (3KB).

This dataset provides the issue category names for merging. Merge via one of the \path{issue_*} variables.



### Variables
\begin{tabularx}{\textwidth}{llX}

\textbf{Variable name} & \textbf{Format} & \textbf{Description} \\

\hline

\path{issue}          &   [integer, 1-23]         &   Issue category code  \\
\path{issue_name}     &   [string]        &   Issue category description  \\


\end{tabularx}

\vfill
### Issue list
```{r echo=TRUE}
partypress_issues <- readRDS("rds/partypress_issues.RDS")
partypress_issues
```

\vfill
\newpage

# Raw texts dataset PARTYPRESS TEXTS
\footnotetext[1]{\label{note1} The text and header of the press releases will be published after permission has been granted by the copyright holders.}

Load files \path{partypress_texts.csv} (561MB) or \path{partypress_texts.RDS} (193MB) (not available as \path{.dta}).

This dataset provides the raw texts of all press releases. The headers are contained in the main dataset.
We provide the texts separately because they use a lot of disk space but some users may not be interested in raw text. Merge via \path{country_name} + \path{id}.

### Variables
\begin{tabularx}{\textwidth}{llX}

\textbf{Variable name} & \textbf{Format} & \textbf{Description} \\

\hline

\path{country_name}          &   [string]         &   Name of the country in small caps  \\
\path{id}                    &   [integer]        &   Press release identifier, unique within \path{country_name}  \\
\path{text}*                  &   [string]         &   Text of press releases in original language)\\

\end{tabularx}

\vfill

### Sample

```{r}
partypress_texts <- readRDS("rds/partypress_texts.RDS")
partypress_texts[sample(1:nrow(partypress_texts), 10), ] %>% 
  mutate(text = substr(text, 1, 60) %>% str_c("(...)")) %>% 
  select(country_name, id, text)
```

\vfill

\newpage
# Aggregated datasets MONTHLY and WEEKLY AGENDAS
Load files \path{monthly_agendas.csv} (20MB)/\path{weekly_agendas.csv} (69MB) or \path{monthly_agendas.RDS} (1MB)/\path{weekly_agendas.RDS} (3MB)  or \path{monthly_agendas.dta} (31MB)/\path{weekly_agendas.dta} (117MB).

### Variables
\begin{tabularx}{\textwidth}{llX}

\textbf{Variable name} & \textbf{Format} & \textbf{Description} \\

\hline

\path{country_name}          &   [string]         &   Name of the country in small caps  \\
\path{parlgov_id}            &   [integer]        &   Party ID (merge with \path{party_id} in ParlGov) \\
\path{party}                 &   [string]         &   Abbreviation of the party name (ParlGov) \\
\path{party_name}            &   [string]         &   Party name (ParlGov) \\
\path{party_name_english}    &   [string]         &   Party name in English (ParlGov) \\
\path{family_name}           &   [string]         &   Party family name (ParlGov) \\
\hline


\multicolumn{3}{l}{only in \path{monthly_agendas}:} \\
\path{month}                 &   [yyyymm]      &   Month   \\
\path{month_start}           &   [date]            &   Date of the first day of the month  \\
\path{month_end}             &   [date]             &   Date of the last day of the month \\
\hline

\multicolumn{3}{l}{only in \path{weekly_agendas}:} \\
\path{calendar_week}         &   [integer, 1-53]  &   Calendar week  \\
\path{week_start}            &   [date]             &   Date of previous Monday  \\
\path{week_end}              &   [date]             &   Date of following Sunday \\

\hline

\path{issue}           &   [integer]        &   Issue category  \\

\path{issue_descr}           &   [string]        &    Issue category description \\

\hline


\path{share_multi}            &   [numeric]        &   Share of press releases of category \path{issue} of all \path{party_sum} predicted from Multilingual Transformer using all labeled docs from all countries \\
\path{share_mono}            &   [numeric]        &   Share of press releases of category \path{issue} of all \path{party_sum} predicted from Monolingual Transformer using all labeled docs from each country in separate models \\
\path{share_ridge}            &   [numeric]        &   Share of press releases of category \path{issue} of all \path{party_sum} predicted from Ridge using all labeled docs from each country in separate models \\
\path{share_super}            &   [numeric]        &   Share of press releases of category \path{issue} of all \path{party_sum} predicted from SuperLearner using all labeled docs from each country in separate models \\



\path{party_sum}            &   [integer]        &   Total number of press releases by this party in this month/week \\


\end{tabularx}

\newpage

### Samples

```{r echo=TRUE}
monthly_agendas <- readRDS("rds/monthly_agendas.RDS")
monthly_agendas[sample(1:nrow(monthly_agendas), 10), ] %>% 
  select(country_name, parlgov_id, party, month, issue, 
         share_multi)

```
\vfill

```{r echo=TRUE}
weekly_agendas <- readRDS("rds/weekly_agendas.RDS")
weekly_agendas[sample(1:nrow(weekly_agendas), 10), ] %>% 
  select(country_name, parlgov_id, party, week_start, 
         issue, share_multi)
```

\vfill